\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-01-13 paper.qmd
Add a figure with how summary works when we have different  benchmark values to remove hexagons with S-curve Conclusion: By comparing MSE values, only phate need to rm lwd hexgons, value 0.24

@@

@@

@@

>>>>

num_bins_vec <- 1:20 ## Number of bins along the x-axis

@@

num_bins_vec <- 1:14 ## Number of bins along the x-axis

@@

num_bins_vec <- 1:18 ## Number of bins along the x-axis

@@

<!--lwd smoothing criteria with s-curve-->

MSE_df_1_lwd <- read_rds("data/s_curve/s_curve_summary_lwd_tsne.rds")
MSE_df_2_lwd <- read_rds("data/s_curve/s_curve_summary_lwd_umap.rds")
MSE_df_3_lwd <- read_rds("data/s_curve/s_curve_summary_lwd_phate.rds")
MSE_df_4_lwd <- read_rds("data/s_curve/s_curve_summary_lwd_trimap.rds")
MSE_df_5_lwd <- read_rds("data/s_curve/s_curve_summary_lwd_pacmap.rds")

MSE_df_lwd <- dplyr::bind_rows(MSE_df_1_lwd, MSE_df_2_lwd, MSE_df_3_lwd, MSE_df_4_lwd, MSE_df_5_lwd)

MSE_df_lwd$method <- factor(MSE_df_lwd$method, levels = c("tSNE", "UMAP", "PHATE", "TriMAP", "PaCMAP"))

## To draw with AIC
aic_plot_lwd <- ggplot(MSE_df_lwd |> dplyr::filter(data_type == "training"), aes(x = benchmark_rm_hex,
                                                                                 y = total_error,
                                                                                 color = method
)) +
  geom_point() +
  geom_line() +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_colour_manual(values = c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("AIC") +
  xlab("Benchmark value")
## Effective number of bins along x-axis

mse_plot_lwd <- ggplot(MSE_df_lwd, aes(x = benchmark_rm_hex,
                                       y = total_mse,
                                       color = method
)) +
  geom_point() +
  geom_line() +
  theme_light() +
  theme(legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_colour_manual(values = c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("MSE") +
  xlab("Benchmark value")

```{r}
#| echo: false
#| warning: false
#| fig-cap: Goodness of fit statistics from different NLDR techniques applied to training S-curve dataset with different benchmark values to remove the low-density heaxgons. What is the effective benchark valuw to remove the low-density heaxgons?
#| label: fig-diagnosticpltScurvelwd
#| out-width: 100%

aic_plot_lwd + mse_plot_lwd +
  plot_annotation(tag_levels = 'a') +
  plot_layout(guides='collect', ncol = 2) &
  theme(legend.position='bottom', plot.tag = element_text(size = 8))
```

### 2024-01-13 paper.tex
Add a figure with how summary works when we have different  benchmark values to remove hexagons with S-curve Conclusion: By comparing MSE values, only phate need to rm lwd hexgons, value 0.24

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, enhanced, frame hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, frame hidden, boxrule=0pt, enhanced, sharp corners, breakable]}{\end{tcolorbox}}\fi

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-diagnosticpltScurvelwd-1.pdf}

\caption{\label{fig-diagnosticpltScurvelwd}Goodness of fit statistics
from different NLDR techniques applied to training S-curve dataset with
different benchmark values to remove the low-density heaxgons. What is
the effective benchark valuw to remove the low-density heaxgons?}
